\plaintitle

### 2016-05-20 cscw/papers/2017/labor/trackingWork.tex
discretization content

% I never talk about factorization it's too soon ahhhh
With piecework and factorization making mass manufacturing more viable,
businesses could produce at scales that were previously unimaginable.
Nevertheless, this approach to labor and the production capacity it offered was not without its hurdles.
One of the issues that challenged mass production at the turn of the \nth{20} century,
as well as today in crowd work and elsewhere,
has been that of ensuring that the quality of the work is sufficiently good.
One of the

@@

\textit{Harken back to piecework
and the instructions that denim workers had to make clothing;
the instructions were clear and scoped enough that you could repeat the task ad infinitum.}

>>>>

Distributing work in method described above may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment or being responsible for driving in a single neighborhood.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable.
Textile work being a salient example,
some seamstresses might be better than others at the same task,
making this framing of the work initially problematic.

A compelling solution emerged in the early \nth{20} century to break tasks down into discrete,
manageable routines that could be taught relatively easily,
and whose work output could be evaluated in abstraction from the rest of the work.
In Ford's assembly line, this meant that workers were not responsible for building a whole car,
but a single very narrowly defined action that needed to be done on every car.

This approach paralleled what would be known as ``Taylorism'',
and its influences can be seen today in crowd work and micro--tasks.
\textit{talk about breaking tasks down both in general (Cheng) and even for the self (Teevan);
horizontal cuts instead of vertical}
\cite{cheng2015break,writingMicroTasks}.
% and might generally be regarded collectively as ``scientific management''
% The compelling solution that emerged in piecework became what we now know as Taylorism;
% rather than

% I never talk about factorization it's too soon ahhhh
% With piecework and factorization making mass manufacturing more viable,
% businesses could produce at scales that were previously unimaginable.
% Nevertheless, this approach to labor and the production capacity it offered was not without its hurdles.
% One of the issues that challenged mass production at the turn of the \nth{20} century,
% as well as today in crowd work and elsewhere,
% has been that of ensuring that the quality of the work is sufficiently good.

@@

% \textit{Harken back to piecework
% and the instructions that denim workers had to make clothing;
% the instructions were clear and scoped enough that you could repeat the task ad infinitum.}
